 

### 2023-04-24 appendix_2.1.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

The health facility data used in our study were obtained from Madagascar's *Gestion du Système d'Information Sanitaire* (GESIS), a Microsoft Access electronic health management information systems database.

While primary, district, and regional referral facilities in Madagascar all reported monthly visits related to mental disorders in GESIS, case definitions varied across facilities of different levels. Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) were only reported among regional referral hospitals and university hospitals; for all other facilities, visit by type of mental heath complaint were reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).

@@

A summary of GESIS data availability is provided in Table S2.1.

@@

After compiling the GESIS data, we translated the case definitions from French to English. The translations are provided in Table S2.2.

@@

Among primary health facilities, we observed that the case definition for mental disorders changed during 2015, alongside the changes in GESIS that enabled disaggregated reporting by sex and greater disaggregation for data by age.

@@

To address heterogeneity in reporting across primary, district, and regional facilities, our analysis constructed a single, summary outcome measure: any mental or neurological disorders reported in a given month by a given facility, irrespective of age and sex. This outcome measure was constructed by grouping our count data by facility and month-year, and then summing the incidence of mental and neurological disorders reported in GESIS within groups, preventing double counting and the inclusion of referrals in the summary measure.

>>>>

The health facility data used in our study were obtained from Madagascar's *Gestion du Système d'Information Sanitaire* (\acr{GESIS}), a Microsoft Access electronic health management information systems database.

While primary, district, and regional referral facilities in Madagascar all reported monthly visits related to mental disorders in \acr{GESIS}, case definitions varied across facilities of different levels. Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) were only reported among regional referral hospitals and university hospitals; for all other facilities, visit by type of mental heath complaint were reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).

@@

A summary of \acr{GESIS} data availability is provided in Table S2.1.

@@

After compiling the \acr{GESIS} data, we translated the case definitions from French to English. The translations are provided in Table S2.2.

@@

Among primary health facilities, we observed that the case definition for mental disorders changed during 2015, alongside the changes in \acr{GESIS} that enabled disaggregated reporting by sex and greater disaggregation for data by age.

@@

To address heterogeneity in reporting across primary, district, and regional facilities, our analysis constructed a single, summary outcome measure: any mental or neurological disorders reported in a given month by a given facility, irrespective of age and sex. This outcome measure was constructed by grouping our count data by facility and month-year, and then summing the incidence of mental and neurological disorders reported in \acr{GESIS} within groups, preventing double counting and the inclusion of referrals in the summary measure.

### 2023-04-24 appendix_2.2.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

We standardized region, district, and commune names in our sample against reference shapefiles to address variations in translation (e.g., "Atsimo" and "Sud" being the Malagasy and French words for "South"), abbreviation (e.g., "St." as an abbreviation for "Saint"), transposition (e.g., "Bevoay Beretra" transposed as "Beretra Bevoay"), accent marks (e.g., "Tovòna" vs. "Tovona"), spacing (e.g., "AmbalapaisoII" vs. "Ambalapaiso II"), separation vs. combination of names (e.g., "Tanambaovatrakaka" vs. "Tanambao Vahatrakaka"), hyphenation (e.g, "Ankiabe Salohy" and "Ankiabe-Salohy"), and spelling (e.g., "Mizilo Gare" vs.	"Mizilo Gara").

@@

We applied an arbitrary restriction to line and polygon groups, such that the length or area, respectively, would not exceed a particular threshold. The threshold for length (`r format(as.numeric(length_lim), big.mark = ",")` km.) was selected to be approximately half the distance of one side of a spatial climate resolution tile (~30 km for ERA-5 data). The threshold for area (`r format(as.numeric(area_lim), big.mark = ",")` km²) was assigned to be the length threshold, squared. Groups that exceeded their respective thresholds were discarded.

@@

Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` km², with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` km². At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` km², all polygon groups fell within the cut-off. Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` km, with a maximum distance of `r format(round(n_max_length), big.mark = ",")` km. At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` km,  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).

@@

While it would be ideal to obtain precise locations for each facility in our sample, for the purposes of our analysis, an approximate location would be sufficient, given the spatial resolution of the climate data we used. The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 900 km² will have the same time series for a given variable. Furthermore, neighboring tiles are unlikely to have extraordinarily different time series, underscoring that close approximate locations would likely result in minimal impact to the analysis versus exact coordinates.

For commune-level facilities, knowing the catchment area may therefore be just as informative as knowing the facility's precise location if the catchment area was sufficiently small. Determining a cut-off was, again, arbitrary; to adopt a conservative threshold, we considered a catchment area small if its area was  no greater than `r format(as.numeric(area_lim), big.mark = ",")` km², which corresponded to approximately `r round(as.numeric(area_lim)/(30*30) * 100,0)`% of the area of a climate data spatial resolution tile (Figure \ref{figure_communes_fokontany}).

@@

>>>>

We standardized region, district, and commune names in our sample against reference shapefiles to address variations in translation (e.g., "Atsimo" and "Sud" being the Malagasy and French words for "South"), abbreviation (e.g., "St." as an abbreviation for "Saint"), transposition (e.g., "Bevoay Beretra" transposed as "Beretra Bevoay"), accent marks (e.g., "Tovòna" vs. "Tovona"), spacing (e.g., "AmbalapaisoII" vs. "Ambalapaiso II"), separation vs. combination of names (e.g., "Tanambaovatrakaka" vs. "Tanambao Vahatrakaka"), hyphenation (e.g., "Ankiabe Salohy" and "Ankiabe-Salohy"), and spelling (e.g., "Mizilo Gare" vs.	"Mizilo Gara").

@@

We applied an arbitrary restriction to line and polygon groups, such that the length or area, respectively, would not exceed a particular threshold. The threshold for length (`r format(as.numeric(length_lim), big.mark = ",")` \acr{km}) was selected to be approximately half the distance of one side of a spatial climate resolution tile (~30 \acr{km} for \acr{ERA5} data). The threshold for area (`r format(as.numeric(area_lim), big.mark = ",")` \acr{km}²) was assigned to be the length threshold, squared. Groups that exceeded their respective thresholds were discarded.

@@

Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` \acr{km}², with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` \acr{km}². At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` \acr{km}², all polygon groups fell within the cut-off. Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` \acr{km}, with a maximum distance of `r format(round(n_max_length), big.mark = ",")` \acr{km}. At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` \acr{km},  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).

@@

While it would be ideal to obtain precise locations for each facility in our sample, for the purposes of our analysis, an approximate location would be sufficient, given the spatial resolution of the climate data we used. The spatial resolution of \acr{ERA5} and \acr{ESA CCI} data is approximately 30 \acr{km}, meaning that all coordinates within a spatial tile of 900 \acr{km}² will have the same time series for a given variable. Furthermore, neighboring tiles are unlikely to have extraordinarily different time series, underscoring that close approximate locations would likely result in minimal impact to the analysis versus exact coordinates.

For commune-level facilities, knowing the catchment area may therefore be just as informative as knowing the facility's precise location if the catchment area was sufficiently small. Determining a cut-off was, again, arbitrary; to adopt a conservative threshold, we considered a catchment area small if its area was  no greater than `r format(as.numeric(area_lim), big.mark = ",")` \acr{km}², which corresponded to approximately `r round(as.numeric(area_lim)/(30*30) * 100,0)`% of the area of a climate data spatial resolution tile (Figure \ref{figure_communes_fokontany}).

@@

 ggsave(filename = paste0("Figure_24.jpg"),
    plot = last_plot(),
    width = 7,
    height = 6,
    bg = "white")

### 2023-04-24 conclusion.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

In Chapter 1, we examined how the global burden is defined, and we proposed an estimation approach to more comprehensively reflect morbidity and loss of life due to suicide and premature mortality attributable to mental disorders. After applying this composite estimation approach to the most recently available estimates from the Global Burden of Disease study, we found that approximately one in 6 disability-adjusted life years (approximately 16%) were due to mental disorders in 2019. We then applied a value of a statistical life year approach to estimate the associated global economic burden. Our findings suggest staggering loses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion USD in 2019. The magnitude of these findings underscores the global scale of impact that mental disorders have and highlights the urgency for research and action to support mental health worldwide.

@@

In Chapter 3, I examined how search data for health symptoms could, in the absence of high frequency surveillance data, provide insight into changes in population mental health during the COVID-19 pandemic. I obtained Google search data from U.S. counties, states, and international trends for over 400 symptoms and used these data to study the immediate and sustained impacts of announcements of the development of safe and effective COVID-19 vaccines in November 2020. I found that searches for anxiety, depression, and major depressive disorder significantly fell after these announcements, and that this decline continued throughout the subsequent weeks. Furthermore, despite the subsequent (and ongoing) politicization of COVID-19 vaccines in the United States, I observed consistency in search density declines for mental health symptoms across red and blue states/counties. The findings speak to the importance of timely and transparent communication in public health, as well as to the potential use of internet search data to investigate changes in population mental health that may be difficult to detect without high frequency data.

>>>>

In Chapter 1, we examined how the global burden is defined, and we proposed an estimation approach to more comprehensively reflect morbidity and loss of life due to suicide and premature mortality attributable to mental disorders. After applying this composite estimation approach to the most recently available estimates from the Global Burden of Disease study, we found that approximately one in 6 disability-adjusted life years (approximately 16%) were due to mental disorders in 2019. We then applied a value of a statistical life year approach to estimate the associated global economic burden. Our findings suggest staggering loses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion \acr{USD} in 2019. The magnitude of these findings underscores the global scale of impact that mental disorders have and highlights the urgency for research and action to support mental health worldwide.

@@

In Chapter 3, I examined how search data for health symptoms could, in the absence of high frequency surveillance data, provide insight into changes in population mental health during the COVID-19 pandemic. I obtained Google search data from \acr{US} counties, states, and international trends for over 400 symptoms and used these data to study the immediate and sustained impacts of announcements of the development of safe and effective COVID-19 vaccines in November 2020. I found that searches for anxiety, depression, and major depressive disorder significantly fell after these announcements, and that this decline continued throughout the subsequent weeks. Furthermore, despite the subsequent (and ongoing) politicization of COVID-19 vaccines in the United States, I observed consistency in search density declines for mental health symptoms across red and blue states/counties. The findings speak to the importance of timely and transparent communication in public health, as well as to the potential use of internet search data to investigate changes in population mental health that may be difficult to detect without high frequency data.

### 2023-04-24 frontmatter.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

I am grateful to the many individuals who have supported and encouraged me throughout my doctoral studies

@@

Across the Charles River are many dear colleagues who have dedicated themselves to ensuring that Harvard feels like home to all its students. To Jackie Yun and Janet Daniels at the GSAS Student Center, and to Sheila Thomas, Katie Saibara, and Karina Gonzalez Herrera of the GSAS Office of Equity, Diversity, Inclusion & Belonging, I wish to express my deepest admiration and appreciation.

@@

 *     *     *
 \vspace{12pt}

@@

>>>>

I am grateful to the many individuals who have supported and encouraged me throughout my doctoral studies.

@@

Across the Charles River are many dear colleagues who have dedicated themselves to ensuring that Harvard feels like home to all its students. To Jackie Yun and Janet Daniels at the Graduate School of Arts and Sciences Student Center, and to Sheila Thomas, Katie Saibara, and Karina Gonzalez Herrera of the Office of Equity, Diversity, Inclusion & Belonging, I wish to express my deepest admiration and appreciation.

@@

@@

\vspace{14pt}

### 2023-04-24 intro.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

Mental health is an essential part of human flourishing. As defined by the World Health Organization (WHO), it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community”.[@worldhealthorganizationComprehensiveMentalHealth2013]

For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are a leading cause of disability,[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] with the Global Burden of Disease (GBD) study estimating that 4.9% of disability-adjusted life years (DALYs) and 14.6% of years lived with disability (YLDs) were attributable to mental disorders in 2019.[@vosGlobalBurden3692020a] Mental disorders are also closely linked to physical health and can be a significant risk factor for premature mortality.[@walkerMortalityMentalDisorders2015] Among patients living with the most severe mental illnesses, premature mortality may reduce life expectancy by as much as 10 to 20 years.[@demooijDyingTooSoon2019]

@@

col_light_blue = "deeppink3"
col_grey = "#CCCCCC"
col_light_grey = "#F2F2F2"

@@

map <- world_map %>%
  filter(admin != "Antarctica") %>%
  full_join(who_gho_data, by = "adm0_a3") %>%
  mutate(fill = ifelse(average < 10,
                       "Fewer than 10 psychiatrists per 100,000 capita",
                       "Others")) %>%
  mutate(fill = ifelse(is.na(fill), "No data", fill)) %>%
  mutate(fill = factor(fill, 
                       levels = c("Fewer than 10 psychiatrists per 100,000 capita", 
                                  "Others",
                                  "No data"))) %>%
  ggplot(aes(geometry = geometry, fill = fill)) +
  geom_sf(color = NA) +
  theme_void() +
  # labs(title = "Availability of psychiastrists",
  #  subtitle = " ") +
  scale_fill_manual(name = "",
                    values = c(col_light_blue, col_grey, col_light_grey)) +
  theme(legend.position = "bottom",
        legend.justification='center',
        legend.direction='horizontal',
        text = element_text(family = "Arial"),
        # plot.title =element_text(size=18, 
        #       face = "bold",
        #       hjust = 0),
        axis.title.x = element_text(color=col_grey, size=10, hjust = 0),
        plot.caption = element_text(hjust = 0, 
                                    vjust = 1,
                                    face = "bold",
                                    size=10))

@@

# Make the plot
circle <- data %>%
  ggplot(aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=category)) +
  geom_rect() +
  # geom_label( x=3.5, aes(y=labelPosition, label=label), size=6) +
  geom_richtext(aes(x = 0,
                    y = 0),
                label = paste0(round(data$fraction[data$category == "A"]*100,0),
                               "%"),
                color = "black", 
                fill = NA,
                label.color = NA,
                size = 10 / .pt,
                hjust = 0.5,
                vjust = .9) +
  coord_polar(theta="y") +
  xlim(c(-1, 4)) +
  theme_void() +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(col_light_blue, col_grey))

@@

@@

The extant and evolving challenges of global mental health, in turn, entail jeopardy to health systems and to the three intrinsic goals of improving health, responsiveness, and financial protection.[@robertsGettingHealthReform2008] According to the WHO’s Mental Health Atlas report from 2020, mental health system governance, capacity, and integration into routine service delivery is fundamentally lacking across nations of all levels of economic development, with only 15% of countries having functional integration of mental health into primary health care.[@worldhealthorganizationMentalHealthAtlas2021] This lack of service delivery echoes a lack of basic epidemiological data,[@steinCrossnationalEpidemiologySocial2017] constraining research and frustrating efforts to respond to mental health needs. Among nations, the Atlas report highlights widening disparities in health system indicators, with worsened gaps in service availability and public health expenditure for mental health between low- and middle-income countries and high-income peers. With respect to health spending, mental health care services in many countries have traditionally relied primarily or exclusively on out-of-pocket payments,[@dixonFinancingMentalHealth2006] resulting in a greater risk of catastrophic health expenditure among households with patients living with a mental disorder. These direct costs, when coupled with the indirect costs of diminished earnings due to disability, may exacerbate conditions of poverty, [@patelPovertyCommonMental2003] which, in turn, may lead to worsening mental health[@lundPovertyCommonMental2010]—feeding a vicious cycle that harms households and nations alike.

A better understanding of the evolving burden and dynamics of global mental health may thus have broad consequences to strengthening health system responses to mental disorders and improving health outcomes for millions of individuals worldwide. Contributing to such an understanding has motivated this dissertation, which takes as its focus different quantitative aspects of the global burden of mental illness—how we measure and evaluate it, how it may be changing, and how novel data sources may help in characterizing it, particularly in the absence of robust, high-frequency epidemiological surveillance. The papers presented in the subsequent three chapters echo the interdisciplinary nature of global mental health, drawing on a broad range of quantitative methods and applying analytic tools and insights from epidemiology, health economics, and econometrics.

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available GBD data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. Using value of statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion USD.

@@

In Chapter 3, I investigated how internet search data for health symptoms might provide high frequency insight into the state of population mental health during the COVID-19 pandemic. Using search data from U.S. counties, states, and international trends, I explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms. I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements. The findings underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

>>>>

Mental health is an essential part of human flourishing. As defined by the \acr{WHO}, it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community”.[@worldhealthorganizationComprehensiveMentalHealth2013]

For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are a leading cause of disability,[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] with the \acr{GBD} study estimating that 4.9% of \acr{DALYs} and 14.6% of \acr{YLDs} were attributable to mental disorders in 2019.[@vosGlobalBurden3692020a] Mental disorders are also closely linked to physical health and can be a significant risk factor for premature mortality.[@walkerMortalityMentalDisorders2015] Among patients living with the most severe mental illnesses, premature mortality may reduce life expectancy by as much as 10 to 20 years.[@demooijDyingTooSoon2019]

@@

col_highlight = "#E4007C"
col_grey = "#CCCCCC"
col_light_grey = "#F2F2F2"

@@

map <- world_map %>%
  filter(admin != "Antarctica") %>%
  full_join(who_gho_data, by = "adm0_a3") %>%
  mutate(fill = ifelse(average < 10,
                       "Fewer than 10 psychiatrists per 100,000 capita",
                       "Others")) %>%
  mutate(fill = ifelse(is.na(fill), "No data", fill)) %>%
  mutate(fill = factor(fill, 
                       levels = c("Fewer than 10 psychiatrists per 100,000 capita", 
                                  "Others",
                                  "No data"))) %>%
  ggplot(aes(geometry = geometry, fill = fill)) +
  geom_sf(color = NA) +
  theme_void() +
  # labs(title = "Availability of psychiastrists",
  #  subtitle = " ") +
  scale_fill_manual(name = "",
                    values = c(col_highlight, col_grey, col_light_grey)) +
  theme(legend.position = "bottom",
        legend.justification='center',
        legend.direction='horizontal',
        text = element_text(family = "Arial"),
        # plot.title =element_text(size=18, 
        #       face = "bold",
        #       hjust = 0),
        axis.title.x = element_text(color=col_grey, size=10, hjust = 0),
        plot.caption = element_text(hjust = 0, 
                                    vjust = 1,
                                    face = "bold",
                                    size=10))

@@

# Make the plot
circle <- data %>%
  ggplot(aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=category)) +
  geom_rect() +
  # geom_label( x=3.5, aes(y=labelPosition, label=label), size=6) +
  geom_richtext(aes(x = 0,
                    y = 0),
                label = paste0(round(data$fraction[data$category == "A"]*100,0),
                               "%"),
                color = "black", 
                fill = NA,
                label.color = NA,
                size = 10 / .pt,
                hjust = 0.5,
                vjust = .9) +
  coord_polar(theta="y") +
  xlim(c(-1, 4)) +
  theme_void() +
  theme(legend.position = "none") +
  scale_fill_manual(values = c(col_highlight, col_grey))

@@

ggsave(filename = paste0("Figure_1.png"), 
    plot = final_figure, 
    width = 13.33,
    height = 6.3,
    bg = "white")

@@

The extant and evolving challenges of global mental health, in turn, entail jeopardy to health systems and to the three intrinsic goals of improving health, responsiveness, and financial protection.[@robertsGettingHealthReform2008] According to the \acr{WHO}'s Mental Health Atlas report from 2020, mental health system governance, capacity, and integration into routine service delivery is fundamentally lacking across nations of all levels of economic development, with only 15% of countries having functional integration of mental health into primary health care.[@worldhealthorganizationMentalHealthAtlas2021] This lack of service delivery echoes a lack of basic epidemiological data,[@steinCrossnationalEpidemiologySocial2017] constraining research and frustrating efforts to respond to mental health needs. Among nations, the Atlas report highlights widening disparities in health system indicators, with worsened gaps in service availability and public health expenditure for mental health between low- and middle-income countries and high-income peers. With respect to health spending, mental health care services in many countries have traditionally relied primarily or exclusively on out-of-pocket payments,[@dixonFinancingMentalHealth2006] resulting in a greater risk of catastrophic health expenditure among households with patients living with a mental disorder. These direct costs, when coupled with the indirect costs of diminished earnings due to disability, may exacerbate conditions of poverty, [@patelPovertyCommonMental2003] which, in turn, may lead to worsening mental health[@lundPovertyCommonMental2010]—feeding a vicious cycle that harms households and nations alike.

A better understanding of the evolving burden and dynamics of global mental health may thus have broad consequences to strengthening health system responses to mental disorders and improving health outcomes for millions of individuals worldwide. Contributing to such an understanding has motivated this dissertation, which takes as its focus different quantitative aspects of the global burden of mental illness—how we measure and evaluate it, how it may be changing, and how novel data sources may help in characterizing it, particularly in the absence of robust, high-frequency epidemiological surveillance. The papers presented in the subsequent three chapters echo the interdisciplinary nature of global mental health, drawing on a broad range of quantitative methods and applying analytic tools and insights from epidemiology, health economics, and econometrics. They further address different dimensions and determinants of population mental health, as illustrated in the conceptual framework shown in Figure \ref{figure_conceptual_framework}, which is based on a model identified by Dykxhoorn et al.[@dykxhoornConceptualisingPublicMental2022]

```{r figure_conceptual_framework, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 8.5, fig.height = 9.5, fig.align='center', out.width = '95%', fig.scap="Conceptual framework for population mental health.", out.extra='', fig.cap="\\label{figure_conceptual_framework}Conceptual framework for population mental health. Original design, based on framework from Dykxhoorn, J., Fischer, L., Bayliss, B. et al. Conceptualising public mental health: development of a conceptual framework for public mental health.BMC Public Health 22, 1407 (2022). https://doi.org/10.1186/s12889-022-13775-9. Creative Commons Attribution 4.0 International License"}

knitr::include_graphics("conceptual_framework_figure.png")

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available \acr{GBD} data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. Using value of statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion \acr{USD}.

@@

In Chapter 3, I investigated how internet search data for health symptoms might provide high frequency insight into the state of population mental health during the COVID-19 pandemic. Using search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms. I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements. The findings underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.
